\documentclass{simplethesisdissertation}
\usepackage{datenumber}
\usepackage{datetime}
\usepackage[en-US]{datetime2}
\usepackage[T1]{fontenc}
\usepackage[italian,english]{babel}
\makeatletter
\makeatother
\title{{\Huge{My Nescafe Story} \linebreak \linebreak \\ \Large{How life killed a Mechanical Engineer}}}
\author{\Huge{{Kaushal Kumar}}}
\date{\texttt{\datedayname, \monthname { }\the\day, \the\year} }
\begin{document}
\maketitle
%%\thispagestyle{empty}
\tableofcontents
%%\mainmatter
\chapter{Nataraja in his own words} \hrulefill
\section{The Anonymous}
\chapter{First Sight} \hrulefill
\section{The Classroom}
It was an usual day when Nataraja was with his classroom kids post his own classes in his own classroom. The kids were yelling and he was trying to control them by engaging them all at a go. Then all of a sudden a face appeared at the door of the classroom with two other female faces. The face was of Gauri, someone who was going to leave the scars in Nataraja's life. \\ \\
Well she was someone who had to make an impact and Nataraja had absolutely no idea that big apocalypse is about to happen. Well there are lot's of things in life that happen and we have no control over them. \\ \\ 
Gauri enters into the classroom and he was going to witness the biggest hitback in his life. Life happens when you are busy making other plans and so does pain. Life was playing a trick and Nataraja was completely unaware of that. \\ \\ 
Nataraja was speelbound with the spark of her eyes. It took him few seconds to grasp the moment and get back. He had never seen anyone having that glow in the eyes. Indeed they were special ones. They were eyes which were made with special attention and care. \\ \\ 
\end{document}